---
title: "The 'apero' package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{apero}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The {apero} package has three purposes. The last one of course is purely recreational and not at all serious.

1. Its "packaging.R" script explains how to build a simple package using "usethis" and "devtools".
2. It shows how to use S3 object oriented programming.
3. How many guests can you place in a room of given length and width, given that each person should be at least some distance (1.5 m, say) away from each other?

## Installation

``` r
library(devtools)
install_github("mayer79/apero", dependencies = TRUE)
```

## Usage 

### Example 1

```{r fig.width = 7}
library(apero)

x <- apero()
summary(x)
plot(x)
plot(x, emo = "wine_glass", color = "red")
```

### Example 2

```{r fig.width = 7}
x <- apero(room_length = 2, room_width = 1)
summary(x)
plot(x)
```
